|

### 2020-03-19 paper/CopyOfpaper.Rmd
getting there

title: |
    Promise and peril: Agnostic identification methods  
    for detecting differential item functioning
subtitle: |
    Ben Stenhaug, Ben Domingue, and Mike Frank  
    Stanford University
abstract: |
  It is well known that likelihood ratio tests (LRT) are effective at detecting differential item functioning (DIF) in item response models. However, to use an LRT, the model needs to be identified so that differences in group ability can be disentangled from potential DIF. We summarize existing agnostic identification (AI) methods and propose a variety of new methods. We conduct a simulation study — which we believe to be more realistic than most DIF simulation studies in the literature — and find that one of the proposed new AI methods, All-others-as-anchors-one-at-a-time (AOAA-OAT), significantly outperforms current methods. We also offer a new method, the equal means, multiple imputation logit graph (EM-MILG), that presents clearly all information about possible DIF, including sampling variability in item parameters, to the analyst. \clearpage <!-- https://tinyurl.com/ybremelq -->
header-includes: 
- \usepackage{amsmath}
- \DeclareMathOperator*{\argmax}{arg\,max} # for gini coefficient
- \DeclareMathOperator*{\argmin}{arg\,min} # for gini coefficient

@@

\clearpage

# Introduction {#intro}

```{r child = "paper_1_intro.Rmd"}
```

# Agnostic identification methods

```{r child = "paper_2a_anchor_items.Rmd"}
```

## Anchor points

```{r child = "paper_2b_anchor_points.Rmd"}
```

# Simulation study

```{r child = "paper_3_sim.Rmd"}
```

\clearpage

<!-- weird formatting that isn't apa I don't think and indentation is weird, solution is to use papaja (look at paper_apa.Rmd) or this might also be helpful https://stackoverflow.com/questions/4073674/how-to-disable-indentation-in-particular-section-in-latex-->

<!-- hopefully all of this below goes away with papaja and other solutions. but remember if it can't editing the latek file is always an option on the final draft! 
https://github.com/haozhu233/kableExtra/issues/214
https://stackoverflow.com/questions/51613152/citing-within-an-rmarkdown-table
https://tex.stackexchange.com/questions/272475/citations-in-tabular-environment-not-working
https://tex.stackexchange.com/questions/359872/is-it-possible-to-use-cite-inside-xtable
https://github.com/yihui/rmarkdown-cookbook/issues/71
-->

>>>>

title: |
    Promise and peril: Agnostic identification methods  
    for detecting differential item functioning
subtitle: |
    Ben Stenhaug, Ben Domingue, and Mike Frank  
    Stanford University
abstract: |
  It is well known that likelihood ratio tests (LRT) are effective at detecting differential item functioning (DIF) in item response models. However, to use an LRT, the model needs to be identified so that differences in group ability can be disentangled from potential DIF. We summarize existing agnostic identification (AI) methods and propose a variety of new methods. We conduct a simulation study — which we believe to be more realistic than most DIF simulation studies in the literature — and find that one of the proposed new AI methods, All-others-as-anchors-one-at-a-time (AOAA-OAT), significantly outperforms current methods. We also offer a new method, the equal means, multiple imputation logit graph (EM-MILG), that presents clearly all information about possible DIF, including sampling variability in item parameters, to the analyst. \clearpage <!-- https://tinyurl.com/ybremelq -->
header-includes: 
- \usepackage{lineno}
- \linenumbers

- \usepackage{amsmath}
- \DeclareMathOperator*{\argmax}{arg\,max} # for gini coefficient
- \DeclareMathOperator*{\argmin}{arg\,min} # for gini coefficient

@@

\begin{table}[H]
\caption{Summary of agnostic identification (AI) methods}
\centering
\begin{tabular}{|p{4cm}|p{6cm}|p{4cm}|}
\toprule

Method & Description & Literature \\

\midrule

all-others-as-anchors (AOAA) & Test if each item has DIF by using all of the other items as anchors (not iterative). & Originally proposed by \cite{lord1980} and formalized by \cite{thissen1993detection} \\\hline

all-others-as-anchors-all-significant (AOAA-AS) & The first iteration is AOAA. All items that test positive for DIF are removed from the anchor set. Continue iterating until no new items test positive for DIF. & Proposed by \cite{drasgow1987study} \\\hline

all-others-as-anchors-one-at-a-time (AOAA-OAT) & The first iteration is AOAA. Only the item that shows the most extreme DIF is removed from the anchor set. Continue iterating until no new items test positive for DIF. & To our knowledge, not proposed or used previously \\\hline

equal means clustering (EMC) & Cluster items based on differences in performance across groups and choose one of the clusters to be the anchor cluster. & Proposed by \cite{bechger2015statistical} and refined by \cite{pohl2017cluster} \\\hline

equal means, multiple imputation logit graph (EM-MILG) & Arbitrarily set both group means to 0, which pushes all group performance differences to the item paramaters, measure variability using multiple imputations, and graph the result. Can be used by an analyst to hand select anchor items & Inspired by pedagolical examples \cite{pohl2017cluster} and \cite{talbot2013taking} \\\hline

multiple imputation logit graph (MILG) & Similar to EM-MILG but used to visualize potential DIF once the model is already identified &  \\\hline

maximizing Gini index (MAXGI) & Arbitrarily set both group means to 0 and then choose an anchor point by maximizing the Gini index & Adapted from work by \cite{strobl2018anchor} \\\hline

minimizing the area between curves (MINBC) & Of the infinite number of model that maximizes the likelihood of the data, choose the one with the minimum total area between the two groups' item characteristic curves & Built on and inspired by work by \cite{raju1988area} and more recently, \cite{chalmers2016might} \\

\bottomrule
\end{tabular}
\label{table:allmethods}
\end{table}
